Making Sequential Programs Deterministic

### 2019-04-01 related.tex
related todo

% https://github.com/TestingResearchIllinois/NonDex/wiki/Supported-APIs
NonDex uses a hand-crafted list of 47 methods (25 unique method names) in
in 13 classes.
This is analogous to our annotations on the JDK\@.
\todo{Say how much code our annotations cover?}
\todo{Check whether our JDK is missing anything they support.}
\todo{Did the NonDex authors contact the maintainers of the tools in which
  they found nondeterminism?}

>>>>

% https://github.com/TestingResearchIllinois/NonDex/wiki/Supported-APIs
NonDex uses a hand-crafted list of 47 methods (25 unique method names) in
in 13 classes.
This is analogous to our annotations on the JDK\@.
\todo{Say how much code our annotations cover?}
\todo{Check whether our JDK is missing anything they support.}
%\todo{Did the NonDex authors contact the maintainers of the tools in which
%  they found nondeterminism?}
\todo{The NONDEX authors didn't contact the maintainers of tools.
From the paper: "NONDEX detected 57 previously unknown
flaky tests in open-source projects and three flaky tests
that have been already fixed by the open-source software
developers."}
